\documentclass[a4wide]{article}
\usepackage{a4wide}
\newcommand{\comment}[1]{{\tt #1}}

\title{System Requirements Specification for:\\ UNTITLED GAME (Project Walrider?)}

\author{Hesham H. Salman \and Jonathon Kissinger \and Sean Mead \and Troy Johnson}

\begin{document}
\maketitle

\section{Introduction}

\subsection{Overall Description}

UNTITLED GAME tracks user inputs and behavioral patterns, and uses this data to determine whether or not the user is likely to have ADHD. This is determined by comparing the user response times and input patterns to those of people with and without ADHD. If the application can determine with a high level of confidence that the user is likely to have ADHD, a suggestion is made to the user to visit a medical professional. \newline \newline
This application is to be used by a number of people with and without ADHD so that we may test its detection algorithms. 

\subsection{Definitions}

Acronyms and abbreviations as applicable

\subsection{References}

References to other documents

\subsection{Overview of Developer's Responsibilities}


Troy Johnson: 
Jonathon Kissinger:
Sean Mead:
Hesham Salman:

Responsibilities in terms of development, installation, training, maintenance
etc.

Eg. The developer is responsible for development, installation,
loading of all the data relating to books in the library,
and training of employees.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{General Description}

\subsection{Product Perspective}

This product will interface with a server, transferring anonymized local user data to a remote server for data processing.


\subsection{Product Functions Overview}

\begin{enumerate}
\item Game: Hurdle Jumper
\item User input tracking and data collection
\item Data processing to determine whether or not the user has ADHD
\item Result generation
\item Comparative analysis of user's data with average user data
\end{enumerate} 

\subsection{User Characteristics}

The users of this application are to be people with and without ADHD. A user survey is conducted at the start of this application such that the results can be calibrated based on the user's age and gender. Of users with ADHD, there is a distinction made between users that are medicated and unmedicated. 

\subsection{General Constraints}

This project is to be completed, including coding, testing, and loading of the database by Nov 30, 2014. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Information Description}

\subsection{Entities and Relationships}

Give a list of entities/relationships that are needed,
and ER diagrams.

\subsection{Data Dictionary}

Give the relations, their attributes, and for each attribute the
type and a description of the attribute.  Here's an example.

\begin{enumerate}
\item customers

\centerline{
\begin{tabular}{|c|c|c|p{3in}|}
\hline 
account\_no& varchar(8)& primary key& account number\\
\hline 
name& varchar(20)& not null& Name\\
\hline 
profession& varchar(10)& not null& Profession\\
\hline 
address& varchar(40)& not null& Address\\
\hline 
email& varchar(40)& -& Email Address \\
\hline 
\end{tabular}
}

\end{enumerate}

\subsection{Data Flow}

Give data flow between major units of your software.
E.g., 
Most useful in case a task has multiple steps requiring interaction
with other software or other humans.
E.g. To purchase a book, user can enter request, department head can
approve, then librarian approves, then order is made.

\section{Functional Requirements}

\begin{enumerate}
\item Introductory User Survey 
\item Home Screen
\item Volume Control
\item Data Collection
\item Game Functionality
\item Data transfer and processing
\item Result display
\end{enumerate} 


\subsection{Introductory User Survey}
The introductory user survey is displayed on first load of the program. It must be completed before the home screen is allowed to display. The introductory user survey establishes information to better understand the user's state: whether or not they have been diagnosed with ADHD (and if they have, whether or not they are currently taking medicine), their age, and their gender. This information is required so that the calculations regarding the likelihood of ADHD are accurate. In the case that the user does not complete the survey, their incomplete survey's state is saved, and will be loaded upon re-launch of the program. 

\subsection{Home Screen}
The home screen must display two navigation options to the user: the option to begin the game and the option to enter the settings pane. In the case that the user does not select an option, the program will remain in the home-screen state. 

\subsection{Volume Control}
Allows the user to toggle audio volume. 

\subsection{Data Collection}
Collects the following usage metrics from the user:
\begin{enumerate}
\item Introductory User Survey
\item Reaction Time
\item Amount Played
\item Number of encounters
\item Average Session Length
\end{enumerate}

Furthermore, error logs are collected in the event of an error.

\subsection{Game Functionality}
The game involves a single character sprite running rightwards, avoiding obstacles which appear at pseudo-random intervals. 

\subsection{Data Transfer and Processing} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{External Interface Requirements}

\subsection{User Interfaces}

This used to be important, and required a user manual giving commands
screen formats, outputs, error messages, etc.
In your case just say the web is used as interface.

\subsection{Hardware Interfaces}

Interfaces with existing as well as new or special purpose hardware.
E.g. smart card reader for authentication.
In your case say no special hardware.

\subsection{Software Interfaces}

List software platforms that are to be supported.

List interfaces with other software packages etc.
Make sure to list all software that you interface with.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Performance Requirements}

Capacity requirements (estimates of no of users, database size, ..)
Response time requirements (for different tasks)
and throughput (estimates of avg/peak number of transactions per minute, etc).
Don't worry about exact numbers but give ballpark figures.

 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Design Constraints}

\subsection{Standards Compliance}

Software development standards asn well as organizational standards
(eg reports, auditing).

In your case, say not applicable.

\subsection{Hardware Limitations}

Requirements on machines, operating systems, storage capacities etc.
This used to be very important, but these days this matters only
for very fast/highthroughput systems, not so much for the things you
are doing.

Fault tolerance and reliability requirements should also be listed here.

In your case this is not considered
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Validation Criteria}

Validation criteria for demonstrating 
successful implementation and user acceptance.  
In general includes classes of tests and expected software response.

E.g. I will load the database with X amount of data for testing,
and an overview of tests you will run.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Other Requirements}

\end{document}
